Stack Safety as a Security Property

### 2020-07-08 main.tex
Reorg done

  %\item As evidence that the property is not too strong\apt{But we add the lazy version because the strict version \emph{is} too strong, in some sense.}, we show that it is
%  realizible by
%  a previously proposed micropolicy enforcement
%  mechanism~(\Cref{sec:micropolicy}). \leo{And it says yes on a
%    substantial body of code}. We also present a variation of the
%  property + policy that is lazy, easier/more efficient to implement,
%  and provably weaker (\Cref{sec:lazy}).
%\item A provably stronger (inductive? step-by-step/stepwise) variant
%  of this property tuned for testing/verification.  We test the whole
%  thing with a cool framework. \bcp{Which section?}
\end{itemize}
\Cref{sec:relwork} discusses related work;
\cref{sec:future} sketches directions for future work.
%
We begin with a running example that we refer
to throughout the paper (\cref{sec:running-example}) and some
technical preliminaries (\cref{sec:prelim}).

\section{Stack {\underline{Un}}safety by Example}
\label{sec:running-example}

We begin with a running example that will serve both to demonstrate several
``stack-unsafe'' behaviors that our stack safety property should prohibit
and to ground the technical presentation in later sections.

\subsection{Running Example}

@@

\subsection{Attacker Model}

@@

\subsection{Unsafe Variations}
\sna{Variations here collides with state variations. I propose substitutions.}
\leo{I agree there is a collision, not sure about ``substitutions''}
\sna{Mutations, drawing from the randomized testing literature?}

The execution trace shown in \cref{fig:running-trace-b} is an example
of a ``stack-safe'' execution: each process interacts only with the
registers, its local stack space and its call frame. In the rest of
this section we will go over examples of unsafe behaviors, before
formally capturing what stack-safe means formally and discussing
enforcement techniques from the literature in later sections. Throughout
the paper examples will be localized modifications of the example, by
substituting an instruction at a given PC, written:
\[\PCname :\mathit{inst}\]

\leo{TODO: Add citations of mitigation techniques}
\rb{And for those techniques, explain how they reflect their motivating
examples. What does each technique do for those examples? How are they
connected to this work?}

\paragraph*{Bad Write}

\[
44 : [\rsp - 5] \leftarrow r_4
%44 : ~ \sw ~ \rsp ~ r_4 ~ \negate 5
\]

Instruction 44 currently is
$ [\rsp - 2] \leftarrow r_4$,
%$\sw ~ \rsp ~ r_4 ~ \negate 2$,
with the
effect of storing the contents of $r_4$ as the result of {\tt h}. If
instead it wrote to location $\rsp - 5$ then it would be overwriting
private data (the return address) belonging to {\tt g}.

\paragraph*{Bad Read}

\[
30 : r_5  \leftarrow [\rsp - 6]
%30 : ~ \lw ~ r_5 ~ \rsp ~ \negate 6
\]

Instruction 30 currently is
$ r_5 \leftarrow [\rsp - 4]$,
%$\lw ~ r_5 ~ \rsp ~ \negate 4$,
with the
effect of loading the argument of {\tt g} to $r_5$. If instead it
loaded the contents of location $\rsp - 6$, it would obtain access
to the value of {\tt main}'s local variable {\tt x}. Worse, since the next instruction
outputs the contents of $r_5$, that value would immediately be made public.

\paragraph*{Bad Control Flow}

\[
5  : \rra \leftarrow \PCname + 1 ; ~ \PCname \leftarrow r_4
%5 : \jalr ~ r_4 ~ \rra ~ 0
\]
If a {\jalr} instruction was added to {\tt main} with its target being
the middle of the code block of {\tt h}.\apt{describe result of this?}

\subsection{Policies}

@@

>>>>

  %\item As evidence that the property is not too strong\apt{But we add the lazy version because the strict version \emph{is} too strong, in some sense.}, we show that it is
%  realizible by
%  a previously proposed micropolicy enforcement
%  mechanism~(\Cref{sec:micropolicy}). \leo{And it says yes on a
%    substantial body of code}. We also present a variation of the
%  property + policy that is lazy, easier/more efficient to implement,
%  and provably weaker (\Cref{sec:lazy}).
%\item A provably stronger (inductive? step-by-step/stepwise) variant
%  of this property tuned for testing/verification.  We test the whole
%  thing with a cool framework. \bcp{Which section?}
\end{itemize}
\Cref{sec:relwork} discusses related work;
\cref{sec:future} sketches directions for future work.
%
We begin with a running example that we refer to throughout the paper
(\cref{sec:running-example}), a description of our threat model
(\cref{sec:threat}) and some technical preliminaries
(\cref{sec:prelim}).

\section{Running Example}
\label{sec:running-example}

\leo{We've said this literally in the previous sentence. What should this intro
  be in the new reorg?}
%We begin with a running example that will serve both to demonstrate several
%``stack-unsafe'' behaviors that our stack safety property should prohibit
%and to ground the technical presentation in later sections.

@@

\section{Threat Model}

\leo{Needs high level signposting, transitions}

@@

@@

% 
%\leo{TODO: Add citations of mitigation techniques}
%\rb{And for those techniques, explain how they reflect their motivating
%examples. What does each technique do for those examples? How are they
%connected to this work?}
% 
%\paragraph*{Bad Write}
% 
%\[
%44 : [\rsp - 5] \leftarrow r_4
%%44 : ~ \sw ~ \rsp ~ r_4 ~ \negate 5
%\]
% 
%Instruction 44 currently is
%$ [\rsp - 2] \leftarrow r_4$,
%%$\sw ~ \rsp ~ r_4 ~ \negate 2$,
%with the
%effect of storing the contents of $r_4$ as the result of {\tt h}. If
%instead it wrote to location $\rsp - 5$ then it would be overwriting
%private data (the return address) belonging to {\tt g}.
% 
%\paragraph*{Bad Read}
% 
%\[
%30 : r_5  \leftarrow [\rsp - 6]
%%30 : ~ \lw ~ r_5 ~ \rsp ~ \negate 6
%\]
% 
%Instruction 30 currently is
%$ r_5 \leftarrow [\rsp - 4]$,
%%$\lw ~ r_5 ~ \rsp ~ \negate 4$,
%with the
%effect of loading the argument of {\tt g} to $r_5$. If instead it
%loaded the contents of location $\rsp - 6$, it would obtain access
%to the value of {\tt main}'s local variable {\tt x}. Worse, since the next instruction
%outputs the contents of $r_5$, that value would immediately be made public.
% 
%\paragraph*{Bad Control Flow}
% 
%\[
%5  : \rra \leftarrow \PCname + 1 ; ~ \PCname \leftarrow r_4
%%5 : \jalr ~ r_4 ~ \rra ~ 0
%\]
%If a {\jalr} instruction was added to {\tt main} with its target being
%the middle of the code block of {\tt h}.\apt{describe result of this?}
